How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-06 tse-paper/content.tex
incl. xcolors in travis
adapted numbers in literature survey part, also moving back duplicates to original duplicate removal within first pass/filter, closes #25

% Todo: Introduction structure
% 0) we introduce & define the problem 1) we survey which techniques
% exist 2) we implement (for a lack of readily available implementations)
% and compare the most promising ones 3) we draw conclusions for when to
% use which technique

@@

\subsection{Study Selection}
% TODO shorten
\Cref{fig:lit-survey} presents an overview of our study selection.
In this first literature overview study on analyzing build logs, we
therefore want to survey as broad a population of scientific material
as possible.
Note that we do not limit our sources to specific
Software Engineering venues, as is often
done~\cite{petersen2015guidelines}, but survey all sources
monitored by Google Scholar, including Bachelor's and Master's theses,
academic slide decks, and books.
We use Google Scholar as opposed to
Scopus or other databases, as it is the search engine for acdemic
articles with the broadest and most current index, including preprints
from sources such as arXiv.
% TODO: maybe remove. this screams snowballing needed
One challenge is that no common
nomenclature has been established yet (in fact, this is one of the
goals of this article).

@@

First, we filtered out articles based on (1) their title and (2) the
contextual information Google Scholar displayed.
We inlcuded only
publications written in a language intelligible to the authors (that
is, English or German), which disregarded fewer than 1\% of search
hits.
Our strategy was to err on the side of
caution, that is rather including a paper than not.
We then unified
the results of the four search queries based on the link as the
identifying element, removing 60 articles that appeared in more than
one search query.
We automatically removed all duplicates and were
left with 259 (17\%) of the original search results.

With these 259 remaining articles, we followed a backward snowball
sampling for related work.
This added three papers (five before
duplicate elimination) to our literature set, coming to a total of 261
articles.
% TODO: update numbers

On the surviving artciles, we did a second filter phase by downloading the
full articles, reading their abstracts, and searching the full text
for the occurrence of ``log''.
If these papers showed traces of
working with build logs, we included them in our survey. In total, we
were left with 90 articles after this search.

\subsection{Article Classification}
Having trimmed down the set of articles, we investigated them in depth.
We kept all articles that use logs from software builds as input to
some kind of process.
we wanted to characterize how researchers use buildlogs as input to
any processes.
We were interesed in
\begin{itemize}
  \item what kind of build logs they are using and the source of these
  logs.
  \item what information they are retrieving from the logs,
  its kind (chunk/classification) and
  what they use the retrieved information for
  \item which technique they are using to process the build logs,
  in how much detail it is described and whether they published their
  tools
\end{itemize}
To objecifiy our data extraction we created a template of the targeted
factors and performed a pilot.
Two authors extracted the data from five articles and we held a
consensus meeting to unify our understanding
of the data extraction template.
The remaining articles were
divided over these two authors.
We inspected the articles as closely as necessary,
starting from occurences of ``log'' or ``build'' within the text.
The full data extraction template and our results of this step can be
found in our replication package~\cite{brandt2020chunk-replication}.

In this pass we further identified x duplicate articles % TODO: {do we push
% those to the last pass?}.
For several cases, multiple articles extended others, though still
reported on
the same work with the respect to processing build logs.
Of these we only considered the earliest article which reported on
the processing
of build logs.

>>>>

% \section{Introduction}
% Todo: Introduction structure
% 0) we introduce & define the problem 1) we survey which techniques
% exist 2) we implement (for a lack of readily available implementations)
% and compare the most promising ones 3) we draw conclusions for when to
% use which technique

@@

\subsection{Study Selection}
% TODO shorten
\Cref{fig:lit-survey} presents an overview of our study selection.
In this first literature overview study on analyzing build logs, we
therefore want to survey as broad a population of scientific material
as possible.
Note that we do not limit our sources to specific
Software Engineering venues, as is often
done~\cite{petersen2015guidelines}, but survey all sources
monitored by Google Scholar, including Bachelor's and Master's theses,
academic slide decks, and books.
We use Google Scholar as opposed to
Scopus or other databases, as it is the search engine for acdemic
articles with the broadest and most current index, including preprints
from sources such as arXiv.
% TODO: maybe remove, this screams snowballing needed
One challenge is that no common
nomenclature has been established yet (in fact, this is one of the
goals of this article).

@@

First, we filtered out articles based on (1) their title and (2) the
contextual information Google Scholar displayed.
We inlcuded only
publications written in a language intelligible to the authors (that
is, English or German), which disregarded fewer than 1\% of search
hits.
Our strategy was to err on the side of
caution, that is rather including a paper than not.
We then unified
the results of the four search queries based on the link as the
identifying element, removing 60 articles that appeared in more than
one search query.
We removed further duplicates based on the title and were
left with 256 (16\%) of the original search results.
% removed duplicates of data extraction pass already here

With these 256 remaining articles, we followed a backward snowball
sampling for related work.
This added five papers (eight before
duplicate elimination) to our literature set, coming to a total of 261
articles.

On the surviving artciles, we did a second filter phase by downloading the
full articles, reading their abstracts, and searching the full text
for the occurrence of ``log''.
If these papers showed traces of
working with build logs, we included them in our survey.
In total, we
were left with 87 articles after this search.

\subsection{Article Classification}
Having trimmed down the set of articles, we investigated them in depth.
We kept all articles that use logs from software builds as input to
some kind of process and excluded another 15 articles.
For several cases, multiple articles extended others, though still
reported on
the same work with the respect to processing build logs.
Of these we only considered the earliest article which reported on
the processing of build logs.
This excluded 11 articles from our survey.
In sum, we further classify 61 articles.

We wanted to characterize how researchers use buildlogs as input to
any processes.
We were interesed in
\begin{itemize}
  \item what kind of build logs they are using and the source of these
  logs.
  \item what information they are retrieving from the logs,
  its kind (chunk/classification) and
  what they use the retrieved information for
  \item which technique they are using to process the build logs,
  in how much detail it is described and whether they published their
  tools
\end{itemize}
To objecifiy our data extraction we created a template of the targeted
factors and performed a pilot.
Two authors extracted the data from five articles and we held a
consensus meeting to unify our understanding
of the data extraction template.
The remaining articles were divided over these two authors.
We inspected the articles as closely as necessary,
starting from occurences of ``log'' or ``build'' within the text.

The full data extraction template and our results of this step can be
found in our replication package~\cite{brandt2020chunk-replication}.
